\LaTeXe\ guide for the Journal of Functional Programming

### 2019-04-30 papers/jfp/7-experience.tex
Fix spacing, add a TODO
Add a reference to Jaskelioff and O’Connor

Assuming the lengths of the lists \hs{[@@k]} and \hs{[@@v]} always match, this
type is isomorphic to \hs{Task}~\hs{Applicative}, and we can define a similar
\hs{Applicative} instance and conversion functions. By describing these types
using \hs{Task} we are able to describe the differences more concisely
(\hs{Monad} vs \hs{Applicative}), use existing literature to determine what is
and isn't possible, and explore other constraints beyond just \hs{Monad} and
\hs{Applicative}.

>>>>

Assuming the lengths of the lists \hs{[@@k]} and \hs{[@@v]} always match, the
data type \hs{Rule}~\hs{k}~\hs{v}~\hs{v} is isomorphic to
\hs{Task}~\hs{Applicative}~\hs{k}~\hs{v}, and we can define a similar
\hs{Applicative} instance and conversion functions. By describing these types
using \hs{Task} we are able to describe the differences more concisely
(\hs{Monad} vs \hs{Applicative}), use existing literature to determine what is
and isn't possible, and explore other constraints beyond just \hs{Monad} and
\hs{Applicative}.

These and other isomorphisms for \emph{second-order functionals}, i.e.
functions of the form

\vspace{1mm}
\begin{center}
\begin{minipage}{0.5\textwidth}
\begin{minted}[xleftmargin=10pt]{haskell}
@\std{forall}@ f. c f => (k -> f v) -> f a
\end{minted}
\end{minipage}
\end{center}
\vspace{1mm}

for various choices of~\hs{c}, are studied in depth by~Jaskelioff and
O’Connor~\shortcite{jaskelioff2015representation}.
